---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---
=====================================================================================================================
```{r}
library(dplyr)
library(ggplot2)
```
# Loading and preprocessing the data

I assume the input file is already in my directory
```{r}
initial_activity <- read.csv("./activity.csv")
```

# What is mean total number of steps taken per day?

## Calculate the total number of steps taken per day.
```{r}
totalstepsperday <- initial_activity %>% group_by(date) %>% summarise(TotalSteps = sum(steps))
```

## For this part of the assignment, you can ignore the missing values in the dataset.
```{r}
totalstepsperday <- subset(totalstepsperday, !is.na(TotalSteps))
```

## Make a histogram of the total number of steps taken each day.
```{r Total number of steps taken each day}
ggplot(totalstepsperday, aes(x=TotalSteps)) + geom_histogram(binwidth = 400) +
        labs(title = "Total Steps taken each day", x = "Number of Steps", y = "Number of days (frequency)")
```

## Calculate and report the mean and median of the total number of steps taken per day.
```{r}
mean_total <- mean(totalstepsperday$TotalSteps)
median_total <- median(totalstepsperday$TotalSteps)
```

The mean is `r as.integer(mean_total)` and the median is `r median_total`.

=====================================================================================================================

# What is the average daily activity pattern?

## Make a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)
```{r Averaged number of steps taken across all days}
averageinterval <- subset(initial_activity, !is.na(steps)) %>% group_by(interval) %>% summarise(AverageSteps = mean(steps))
ggplot(averageinterval, aes(x=interval, y=AverageSteps)) + geom_line() +
        labs(title = "Averaged number of steps taken across all days", x = "5-minute intervals", y = "Averaged Steps")
```

## Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?
```{r}
max_interval_steps <- averageinterval[which.max(averageinterval$AverageSteps),1]
max_steps <- max(averageinterval$AverageSteps)
```
The interval `r max_interval_steps` contains the maximum number of steps: `r max_steps`

=====================================================================================================================

# Imputing missing values


=====================================================================================================================

# Are there differences in activity patterns between weekdays and weekends?
